\chapter{Blue Flames}

In a quitet basement somewhere in Dayton, Ohio, two young students are working
into the night on a computer. No, this is not a fancy desktop or laptop
computer. It is a simple machine designed to help one of the students learn how
to program in assembly language.

Ada is the student who is building the computer, and her friend, Alan, is
helping her get the critter running. Ada has managed to come up with a nice case
for her machine. The sides of the case are cherry wood which she will finish
off later to make things look nice. The actual case is a bent piece of aluminum
sheet metal she convinced a local automotive body shop to fabricate for her.

The goal this evening is to power the gadget up. Alan is working on wiring a
power supply for the machine that will be bolted inside the case. A switch will
be attached to the sheet metal cabinet along with a keypad and an LED display. 

Ada is bolting a small printed circuit board to the bottom of the case. This
board comprises a complete 8-bit computer system. It is not fancy, nor is it
very powerful, but it will be sufficient for Ada's goal. Alan is wiring up the
power supply and the switch. Both of them work together to get everything
installed in the case, ready for the first power-up!

The evening wears on, and things are getting close to ready. Another student,
Nick, wanders down the stairs into the basement.

"Hey Ada, have you got the thing powered up yet?"

"Just about. Alan is almost finished with the power supply."

Alan puts a screwdriver down on the table.

"Ready for the first test. Ada, you do the honors!"

Ada reaches a nervous hand toward the switch. All three of them hold their
breath. Ada flips the switch.

A brief flash of light is seen inside the case, and the lights go out!

In the darkness, Nick mutters "I guess you flunked the Blue Flame test!"

